---
title: "`r {source('_setup.R'); tr('about.title')}`"
---

```{r}
#| label: setup
#| include: false
## About (SPEC.md S7.1): methodology, the declared limitations of S10, the
## licence and a link to the source.
##
## The five limitation items are NORMATIVE. SPEC.md S10 requires them
## published in full and in both languages; they are emitted as Markdown so
## that inline code and em dashes survive, under explicit,
## language-independent anchors `#lim-1` .. `#lim-5`. Those anchors are the
## one-click target S7.2 demands from every download figure, so they must not
## be renamed.
source("_setup.R")

meta <- zb_json("meta")
limit_ids <- as.character(1:5)
source_ids <- c("downloads", "versions", "checks", "archive", "activity", "traffic", "academic")
```

```{r}
#| label: header
#| results: asis
zb_out(zb_page_header("about.html", zb_get(meta, "latest_data_date")))
```

`r tr("about.lead")`

## `r tr("about.purpose.title")`

`r tr("about.purpose.body")`

## `r tr("about.method.title")`

`r tr("about.method.body")`

`r tr("about.method.curation")`

`r tr("about.method.retention")`

`r tr("about.method.privacy")`

### `r tr("about.sources.title")`

```{r}
#| label: sources
#| results: asis
table <- data.frame(
  name = vapply(source_ids, function(id) tr(paste0("about.src.", id, ".name")), character(1)),
  endpoint = vapply(
    source_ids,
    function(id) zb_md_inline(tr(paste0("about.src.", id, ".endpoint"))),
    character(1)
  ),
  auth = vapply(source_ids, function(id) tr(paste0("about.src.", id, ".auth")), character(1)),
  retro = vapply(source_ids, function(id) tr(paste0("about.src.", id, ".retro")), character(1)),
  limit = vapply(source_ids, function(id) tr(paste0("about.src.", id, ".limit")), character(1)),
  stringsAsFactors = FALSE
)
zb_out(zb_table(
  table,
  labels = c(
    tr("about.sources.col.source"), tr("about.sources.col.endpoint"),
    tr("about.sources.col.auth"), tr("about.sources.col.retro"),
    tr("about.sources.col.limit")
  ),
  label = tr("about.sources.title"),
  align = c("l", "l", "l", "l", "l"),
  raw = "endpoint",
  row_header = TRUE
))
```

## `r tr("about.limits.title")` {#limitations}

`r tr("about.limits.lead")`

```{r}
#| label: limitations
#| results: asis
# Emitted as Markdown, not as an HTML block: these paragraphs carry inline
# code and em dashes that Pandoc must render. The explicit `{#lim-N}` anchors
# are identical in both languages, so a link from a chart on either site
# lands on the same item.
for (id in limit_ids) {
  cat(
    "\n### ", id, ". ", tr(paste0("about.limit.", id, ".title")),
    " {#lim-", id, "}\n\n",
    tr(paste0("about.limit.", id, ".body")), "\n\n",
    sep = ""
  )
}
```

## `r tr("about.nongoals.title")`

`r tr("about.nongoals.modelling")`

`r tr("about.nongoals.commits")`

`r tr("about.nongoals.thirdparty")`

## `r tr("about.license.title")`

`r tr("about.license.body")`

## `r tr("about.source.title")`

`r tr("about.source.body")`

- [`r tr("about.source.link_label")`](https://github.com/evandeilton/prod-monitor)
- [`r tr("about.source.issues_label")`](https://github.com/evandeilton/prod-monitor/issues)

`r tr("about.source.issues_body")`

## `r tr("about.build.title")`

```{r}
#| label: build
#| results: asis
build <- data.frame(
  field = c(
    tr("about.build.generated"), tr("about.build.latest"),
    tr("about.build.schema"), tr("about.build.package"),
    tr("about.build.retention")
  ),
  value = c(
    zb_datetime(zb_get(meta, "generated_at")),
    zb_date(zb_get(meta, "latest_data_date")),
    zb_int(zb_get(meta, "schema_version")),
    as.character(zb_get(meta, "package_version", tr("common.unknown"))),
    zb_int(zb_get(meta, "retention_months"))
  ),
  stringsAsFactors = FALSE
)
zb_out(zb_table(
  build,
  labels = c(tr("about.build.col.field"), tr("about.build.col.value")),
  label = tr("about.build.title"),
  align = c("l", "l"),
  row_header = TRUE
))

counts <- meta$row_counts
latest <- meta$latest_data_date_by_table
if (length(counts)) {
  tables <- names(counts)
  rows <- data.frame(
    table = paste0("<code>", zb_esc(tables), "</code>"),
    rows = zb_int(unlist(counts[tables], use.names = FALSE)),
    latest = zb_date(vapply(
      tables,
      function(nm) {
        value <- latest[[nm]]
        if (is.null(value) || length(value) == 0L) NA_character_ else as.character(value)
      },
      character(1)
    )),
    stringsAsFactors = FALSE
  )
  zb_out(zb_table(
    rows,
    labels = c(
      tr("about.build.col.table"), tr("about.build.col.rows"),
      tr("about.build.col.latest")
    ),
    caption = tr("about.build.rows.title"),
    align = c("l", "r", "l"),
    raw = "table"
  ))
}
```
